Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Added code to imperfectly merge the retro graphs together

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))

@@

#figure1 <- multi_panel_figure(columns = 3, rows = 3, panel_label_type = "none")
#figure1

#figure1 %>% 
#  fill_panel(retro_age_plot, column = 1, row = 1) %>% 
#  fill_panel(retro_gender_plot, column = 2, row = 1) %>% 
#  fill_panel(retro_employ_plot, column = 3, row = 1) %>% 
#  fill_panel(retro_ethnicity_plot, column = 1:3, row = 2) %>% 
#  fill_panel(retro_diagnosis_plot, column = 1:3, row = 3)

>>>>

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, 
                                 vjust = 0.5,
                                 size = 8)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))

@@

#Adding any more makes it look awful
ggarrange(retro_age_plot, retro_gender_plot, retro_employ_plot,
          labels = c("", "", ""),
          ncol = 2, nrow = 2)

ggarrange(retro_diagnosis_plot, retro_ethnicity_plot,
         labels = c(""),
         ncol = 2, nrow = 1)
